---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# forImage

The goal of `forImage` is to facilitate foraminiferal test measurement and biomass estimation.

The package is proposed as an alternative to manual and/or multi-software dependent methods for biometry and biomass estimation. 

## Installation

The package **requires** Python >= 3.5. 

You can install `forImage` from github with:

```{r installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ThaiseRF/forImage")
```


Use `install_measure()` to install all Python modules dependencies at once in a virtual environment. 
This function is a wrapper of [reticulate py_install()](https://rstudio.github.io/reticulate/reference/py_install.html) and requires a conda installation on Windows. 


If an error in [read.dcf(path)](https://github.com/r-lib/devtools/issues/1978#issuecomment-460685615) appears during the installation: 


```{r installation2, eval = FALSE}
devtools::install_github("r-lib/remotes")
#Restart R
devtools::install_github("ThaiseRF/forImage")
```

